---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# capratTX

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/pnnl/capratTX.svg?branch=master)](https://travis-ci.com/pnnl/capratTX)
[![DOI](https://zenodo.org/badge/304059832.svg)](https://zenodo.org/badge/latestdoi/304059832)
<!-- badges: end -->



The goal of `capratTX` is to simulate water storage reservoirs providing cooling water to thermal power plants in the ERCOT.

## Contact
- Please use [issues](https://github.com/pnnl/capratTX/issues) for Q & A.
- For other information please contact Sean Turner (sean.turner@pnnl.gov)

## Data requirements

You must download the [ERCOT Reservoir Watershed Delineations and Inflow Scenarios](https://zenodo.org/record/4273147#.X8q-Vy9h1TY) data files to run this software.

## Installation

You can install the development version of `capratTX` using `devtools`:

``` r
library(devtools)
install_github("pnnl/capratTX")
```

## Usage
Start by loading the library and setting the data path:
```{r}
library(capratTX)
data_path <- "your_directory/ERCOT Reservoir Watershed Delineations and Inflow Scenarios/"
```
```{r, show = F}
data_path <- "../../WECC-ERCOT/ERCOT/data/ERCOT Reservoir Watershed Delineations and Inflow Scenarios/"
```

Calibrate reservoirs and save a parameter file (calibration may take a minute or two reservoir operating functions are optimized):
```{r}
calibrate_all_reservoirs(data_path) -> calibrated_parameters
head(calibrated_parameters)
readr::write_csv(calibrated_parameters, "params.csv")
```


To simulate all dams with the calibrated rules under a given period ("baseline" or "future"):
```{r}
simulate_gcm_inflows_all_dams(data_path, period = "future",
                              params_path = "params.csv") -> sim_data
head(sim_data)
```

Plot storage projections for a particular reservoir:

```{r}
library(ggplot2)
library(dplyr)

sim_data %>% 
  # select reservoir desired
  filter(reservoir == "Travis") %>% 
  # get annual minimums
  group_by(reservoir, gcm, year) %>% 
  summarise(s_min = min(s_sim)) %>% 
  ungroup() %>% 
  ggplot(aes(year, s_min, col = gcm)) +
  geom_line() +
  labs(y = "Minimum storage level (MCM)", x = NULL)

```





